Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-11 R0V0.tex
Modified notation of Xi set

For each index $i\in\mathbb{N}_{[1,N]}$, define the sets 
\begin{subequations}
	\begin{equation*}
		\mathscr{K}_Y(i)=\{j\in \mathbb{N}_{[1,N]}\setminus\mathscr{K}(i):Y_{ij}\equiv0\}
	\end{equation*}
	and
	\begin{align*}
		\Xi_Y=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}:\text{the}\ i\text{-th row}\ Y_i\ \\
		\text{has the properties}\ \mathscr{K}_Y(i)\ &\text{and}\ \mathscr{K}(i)\}.
	\end{align*}
\end{subequations}
Note that the set $\mathscr{K}_Y(i)$ is the set index for which the corresponding columns of the row-vector $Y_i$ are zero. By definition, this set is the complement of $\mathscr{K}(i)$. Consequently, given an index $j\in\mathscr{K}_Y$ and $W$ is diagonal, the $i$-th line of the vector $YW^{-1}\delta_x$ does not depend on $j$-th component of the vector $\delta_x$. As remarked in \cite{Tanaka2011}, the constraint ``$Y\in\Xi_Y$'' is linear.

\begin{theorem}\label{thm:main result}
	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
\end{theorem}

\begin{proof}[Proof of Theorem \ref{thm:main result}]
	By assumption, the functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m$ form a solution to the MI \eqref{eq:MI formulation}. Apply the coordinate change $\eta=M\delta$ and define the matrices $W=M^{-1}$ and $K=YW^{-1}$. Since $W$ is diagonal, the structure of $Y$ is preserved and, consequently, $K\in\Xi_Y$.

@@

Consider a graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network \eqref{eq:general system}. A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$. A \emph{clique tree} is a tree that has cliques as its nodes. An algorithm to compute the number of cliques is provided in \cite{BronKerbosch1973}.

>>>>

Following the notation introduced in \cite{Tanaka2011}, for each index $i\in\mathbb{N}_{[1,N]}$, define the set 
\begin{subequations}
	\begin{align*}
		\Xi=&\ \{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |\mathbin{\mathtt{col}}(Y,j)\in\mathbf{C}_j,\\
		&\ \arg(Y_{ij})\in\mathbf{X}_k,\forall i\in\mathbb{N}_{[1,m]},\forall j\in\mathbb{N}_{[1,n]},\\
		&\ k\in\mathbb{N}_{[1,N]}\}\;,
	\end{align*}
\end{subequations}
where $\mathbin{\mathtt{col}}(Y,j)$ stands for the $j$-th column of the matrix $Y$, the set $\mathbf{C}_j$ is the space spanned by the sparsity vector $v_j\in\mathbb{R}^{n}$, and the set $\mathbf{X}_k$ is the space spanned by components of $x$ defined by the set $\mathscr{K}(k)$.

The set $\Xi$ defines the topology of the differential feedback law to be designed for system~\eqref{eq:general system:differential} and the dependence of each element of the matrix $Y$ on the state-space variables. Note that, whenever system \eqref{eq:general system} is linear, the set $\mathbf{X}_i$ is empty, for all indexes $i\in\mathbb{N}_{[1,N]}$, and the set $\Xi$ reduces to the set $\mathcal{K}$ defined in \cite{Tanaka2011}.

In case of full decentralization with $n_i=m_i=1$, for every index $i\in\mathbb{N}_{[1,N]}$,  the set $\Xi$ is defined with $\mathbf{C}_j=\{e_j\}$, $\mathscr{K}(i)=\{i\}$ and $\mathbf{X}_i=\{x_i\}$.

\begin{theorem}\label{thm:main result}
	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
\end{theorem}

\begin{proof}[Proof of Theorem \ref{thm:main result}]
	By assumption, the functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m$ form a solution to the MI \eqref{eq:MI formulation}. Apply the coordinate change $\eta=M\delta$ and define the matrices $W=M^{-1}$ and $K=YW^{-1}$. Since $W$ is diagonal, the structure of $Y$ is preserved and, consequently, $K\in\Xi$.

@@

Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network \eqref{eq:general system}. A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$. A \emph{clique tree} is a tree that has cliques as its nodes.

\begin{proposition}\label{prop:}
	Let $p\in\mathbb{N}_{>0}$ be the number of cliques of the graph $\mathscr{G}$. Then, the MI~\eqref{eq:MI formulation} can be decomposed into $p$ matrix inequalities with smaller dimension.
\end{proposition}

An algorithm to compute the number of cliques is provided in \cite{BronKerbosch1973}.
